Diagnosis_Vis

### 2023-04-30 Diagnosis_Vis.Rmd
Co-occuring disorders plot!

                      ifelse(Trauma_D == 1, "Stress and Trauma",

@@

                    ifelse(  GAD_C ==1 | Panic_C == 1 | PanicAgor_C == 1 | Agoraphobia_C == 1 |
                        Social_C == 1 | Specific_C == 1, 1, 0)),

@@

                    ifelse(MDD_C ==1 | Bipolar1_C == 1 | Bipolar2_C == 1 | Dysthymia_C == 1, 1, 0)),

@@

                    ifelse(Alcohol_C == 1 | Drug_C ==1, 1, 0)),

@@

                    ifelse(PTSD_C == 1 | Adjustment_C ==1, 1,0)),

@@

                    ifelse(Schiz_C == 1 | Schizaff_C == 1,1,0)),

@@

                    ifelse(Anorex_C == 1 | Bulim_C == 1 | Binge_C == 1, 1,0)),

@@

                    ifelse(Somat_C == 1 | UndiffSoma_C == 1| Hypochondriasis_C ==1, 1,0)),

@@

@@

>>>>

                      ifelse(Trauma_D == 1, "Trauma",

@@

                    ifelse( GAD_P !=1 & GAD_C ==1 | 
                        Panic_P != 1 & Panic_C == 1 | 
                        PanicAgor_P != 1 & PanicAgor_C == 1 | 
                        Agoraphobia_P != 1 & Agoraphobia_C == 1 |
                        Social_P != 1 & Social_C == 1 | 
                        Specific_P != 1 & Specific_C == 1, 1, 0)),

@@

                    ifelse( MDD_P != 1 & MDD_C == 1 |
                        Bipolar1_P != 1 & Bipolar1_C == 1 | 
                        Bipolar2_P != 1 &  Bipolar2_C == 1 | 
                        Dysthymia_P != 1 & Dysthymia_C == 1 , 1, 0)),

@@

                    ifelse(Alcohol_P != 1 & Alcohol_C == 1 | 
                        Drug_P != 1 & Drug_C ==1, 1, 0)),

@@

                    ifelse(PTSD_P != 1 & PTSD_C == 1 | 
                        Adjustment_P != 1 & Adjustment_C ==1, 1,0)),

@@

                    ifelse(Schiz_P != 1 & Schiz_C == 1 | 
                        Schizaff_P != 1 & Schizaff_C == 1,1,0)),

@@

                    ifelse(Anorex_P != 1 & Anorex_C == 1 | 
                        Bulim_P != 1 & Bulim_C == 1 | 
                        Binge_P != 1 & Binge_C == 1, 1,0)),

@@

                    ifelse(Somat_P != 1 & Somat_C == 1 | 
                        UndiffSoma_P != 1 & UndiffSoma_C == 1 | 
                        Hypochondriasis_P != 1 &  Hypochondriasis_C == 1, 1,0)),
                  OCD_Co_C = as.factor(
                    ifelse(OCD_P != 1 & OCD_C == 1,1,0)),
                  BPD_Co_C = as.factor(
                    ifelse(BPD_P != 1 & BPD_C ==1,1,0)),

@@

view(Mothership)

@@

```{r}
ggplot(data = subset(Mothership_Diag, !is.na(Disorder_Type)),mapping = aes(x = Disorder_Type, fill=Disorder_Type))+
  geom_bar()+
  ggtitle("Frequency of Psychiatric Disorder Subtypes") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Psychiatric Disorder Subtype")+
  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,3500))+
  coord_flip()
```

```{r}
library(dplyr)
library(tidyr)

Mothership_Current_Long <- Mothership %>%
  pivot_longer(
    cols=c(Anxiety_C, Mood_C, Substance_C, Trauma_C, Psychotic_C, Eating_C,  Somatic_C, OCD_Co_C, BPD_Co_C),
    names_to = 'Disorder_Present'
  ) %>%
  filter(value != 0) %>%
  select(!value)  %>%
  filter(!is.na(Disorder_Present))%>%
  filter(!is.na(Disorder_Type))

## Figure out how to plot these two

Mothership_Current_Long %>%
  ggplot(aes(x = Disorder_Type, y = Disorder_Present, color = Disorder_Type)) +
  geom_count(alpha = .5)+
  scale_size_area(max_size = 20) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
    legend.position = "none") +
  scale_y_discrete(labels=c("Trauma_C" = "Co Trauma", 
                            "Substance_C" = "Co Substance Use",
                            "Somatic_C" = "Co Somatic",
                            "Psychotic_C" = "Co Psychotic",
                            "OCD_Co_C" = "Co OCD",
                            "Mood_C" = "Co Mood",
                            "Eating_C" = "Co Eating",
                            "BPD_Co_C" = "Co BPD",
                            "Anxiety_C" = "Co Anxiety")) +
  labs(
    title = "Number of Co Occuring Psychiatric Diosrders per Primary Diagnosis",
    subtitle = "Grouped into subtypes of DSM diagonsis",
    y = "Co-Occuring Psychiatric Disorder",
    x = "Primary Psychiatric Diagnosis"
  )
